Efficient Handling of String-Number Conversion

### 2020-03-30 final-version/evaluation.tex
little things in final cersion

	\item \changed{ LeetCode is from running PyEx over some sample code collected from the LeetCode~\cite{LeetCode} website, including functions that check if a string is a valid IPv4 or IPv6 address, sum up two binary numbers, check if an input string is an abbreviation of another input string, and decode a sequence of digits to strings according to a given mapping.}

>>>>

	\item \changed{ LeetCode is from running PyEx over a sample code collected from the LeetCode~\cite{LeetCode} website, including functions that check whether a string is a valid IPv4 or IPv6 address, sum up two binary numbers, check whether an input string is an abbreviation of another input string, and convert a sequence of digits to a string according to a given mapping.}

### 2020-03-30 final-version/main.tex
little things in final cersion

However, the formula is satisfiable when $x=``00010"$. Observe that $\sti{``00010"}=10$ \changed{since PFAs accept  numeric words with least significant bit first}. The key is that even for a bounded integer, the corresponding numeral can be of an unbounded length with arbitrarily many trailing `$0$'s at the front. All numbers with up to $m$-digits can be however still handled without having to solve exponential constraints. It is enough to equip the initial state of the PFA with a  $0$-self-loop.

@@

\changed{
The most relevant work to ours is the FA-based approach~\cite{abdulla2018trau} that projects the solution space of variables to a generalization of flat automata. The main difference is that our approach works fully symbolically, which is enabled by to the ideas of using integer variables as characters and hence PFAs. The use of integer variables as characters allows our approach to handle string-number constraints efficiently -- the values and number of occurrences of those variables can be directly convert to a number in a linear formula.

The straightforward extension of existing FA based techniques boils down to solving the satisfiability problem of integer polynomial-exponential constraints, whose decidability is still open (Section~\ref{section:s2i}).

In principle, we can also extend FA-based solvers to support string-number conversion, but PFA are much more efficient. Extending FA-based approach to support string-number conversion would require multiple if-then-else statements (e.g., saying that if a transition labeled `0' is taken, then the corresponding number is $0$), which introduces a significant amount of additional predicates that the DPLL engine needs to decide their value. We have confirmed this in our preliminary experiment.}

>>>>

However, the formula is satisfiable when $x=``00010"$. Observe that $\sti{``00010"}=10$ \changed{since PFAs accept  numerals with the least significant bit first}. The key is that even for a bounded integer, the corresponding numeral can be of an unbounded length with arbitrarily many trailing `$0$'s at the front. All numbers with up to $m$-digits can be however still handled without having to solve exponential constraints. It is enough to equip the initial state of the PFA with a  $0$-self-loop.

@@

\changed{
The most relevant work to ours is the FA-based approach~\cite{abdulla2018trau} that projects the solution space of variables to a generalization of flat automata. The main difference is that our approach works fully symbolically, which is enabled through using integer variables as characters and hence PFAs. The use of integer variables as characters allows our approach to handle string-number constraints efficiently -- the values and number of occurrences of those variables can be directly converted to numbers in a linear formula.

%HERE
The straightforward extension of existing FA based techniques boils down to solving the satisfiability problem of integer polynomial-exponential constraints, whose decidability is still open (Section~\ref{section:s2i}).

In principle, FA-based solvers can be extended to support string-number conversion too, but PFA are much more efficient. Extending FA-based approach would require multiple if-then-else statements (e.g., saying that if a transition labeled `0' is taken, then the corresponding number is $0$), which introduces a significant amount of additional predicates that the DPLL engine needs to evaluate. We have confirmed this in our preliminary experiment.}
